Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-07 paper.tex
Reviewing introduction, leaving a comment.

In general, forecasting the sales of cultural products can
only be based on the knowledge obtained from sales of other, similar, ones,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, making accurate
estimations of future sales of the new product is quite difficult, and
extremely important, so that production runs follow predicted sales.  
Indeed, several studies have demonstrated that improving sales
predictions, that is reducing the error in estimated sales, results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}, so not only cost
associated to the book itself are associated, but also the whole
production process.

@@

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=metodologia.eps,width=5.5cm}
\caption{Steps followed in the proposed methodology.}
\label{fig:methodology}
\end{center}
\end{figure}

>>>>

In general, forecasting the sales of cultural products can
only be based on the knowledge obtained from sales of other, similar, ones,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, making accurate
estimations of future sales of the new product is quite difficult, and
extremely important, so that production runs follow predicted sales.  
Indeed, several studies have demonstrated that improving sales
predictions, that is reducing the error in estimated sales, results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}, so not only cost
associated to the book itself are associated,
% (Paloma) I was about to change this second "associated" for "affected" (seems the right thing to do). However, what's after this comma is also confusing, given that we already said that is affects to the whole production process. Maybe who wrote this should re-think what he/she meant to say here and change it.
 but also the whole
production process.

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=metodologia.eps,width=5.5cm}
\caption{Steps followed in the proposed methodology.}
\label{fig:methodology}
\end{center}
\end{figure}
